An Analysis on the Impact of Local Food Choices

### 2020-03-21 paper_knew.Rmd
Changed wording

@@

## Exploratory Data Analysis 
Using multiple linear regression, we are interested in predicting the Percentage Eligibility of Students in the Free Lunch program (out of the total number of students attending school). The independent variables we are interested in are the following:

  - a
  - b
  - c
  - d
  - e
  - f
  - g
  - h
  - i 
  - j
  - k
  - l

@@

>>>>

The SNAP and WIC are two different food assistance programs at the county level. SNAP provides recipients the ability to purchase discounted food from a variety of retail establishment while the WIC program focuses on providing specific assistance  to malnourished and impoverished women, children and infants during important developmental stages. Thus WIC is more exclusive than SNAP.

@@

## Exploratory Data Analysis 
Using multiple linear regression, we are interested in predicting the Percentage Eligibility of Students in the Free Lunch program (out of the total number of students attending school). The independent variables we are interested in are listed above.

@@

## Are there any group of factors that predict eligibility in the school free lunch program ?
Using a linear regression we are able to narrow down on a mix of child poverty-related independent variables as well as some food access variables (grocery stores, full service restaurants, convenience stores, acres of vegetables harvested) as well as some assistance variables (WIC and SNAP beneftis and redemptions) that determine the eligibility of participation in the FLP at the county level. The details of these associations are in the model evaluation section above. We cannot make a causal inference about this regression.
